The gobba functional programming language.\\WORK IN PROGRESS DRAFT

### 2020-01-19 paper/paper.tex
paper and readme

%% Language and font encodings. This says how to do hyphenation on end of lines.
\usepackage[english]{babel}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{listings}
\usepackage{xcolor}
\usepackage{caption}
\usepackage{mathtools}
\usepackage{amsthm}
\usepackage[title]{appendix}
\usepackage{collectbox}
%\usepackage{tgpagella} % text only
%\usepackage{mathpazo}
\usepackage{stix2}

@@

%% Useful packages
\usepackage{graphicx} %allows you to use jpg or png images. PDF is still recommended
\usepackage[colorlinks=False]{hyperref} % add links inside PDF files
\usepackage{amsmath}  % Math fonts
\usepackage{amsfonts} %
\usepackage{amssymb}  %

@@

%% Citation package
%\usepackage[authoryear]{natbib}
\bibliographystyle{unsrt}
%\setcitestyle{authoryear,open={(},close={)}}

@@

\begin{abstract}
\textbf{gobba} is a dynamically typed and purely functional interpreted
programming language. Based on Professors Gianluigi Ferrari and Francesca Levi's
minicaml interpreter example, the goal for gobba is to be a practical language with
built in support for scientific computing, solving some of the problems that
exist in other dynamically typed interpreted languages like python and Javascript. It is an
interpreted language heavily inspired from the OCaml, Haskell and Scheme
languages, with static (lexical scoping), a simple but effective module system,
eager and lazy evaluation and a didactical REPL that can show each AST
expression and each evaluation step.
\end{abstract}

@@

\section{Syntax and Parser}
Lexing is achieved with \texttt{ocamllex}, the default tool for generating
scanners in OCaml.
The parser is realized with the \textbf{Menhir} parser generator, and is
documented using \textbf{Obelisk}, which generates a clean text file
containing the language grammar, available in Appendix \ref{grammar}.

>>>>

%% Language and font encodings. This says how to do hyphenation on end of lines.
\usepackage[english]{babel}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{listings}
\usepackage{xcolor}
\usepackage{caption}
\usepackage{mathtools}
\usepackage{amsthm}
\usepackage[title]{appendix}
\usepackage[nottoc]{tocbibind}
\usepackage{collectbox}
%\usepackage{tgpagella} % text only
%\usepackage{mathpazo}
\usepackage{stix2}

@@

%% Useful packages
\usepackage{graphicx} %allows you to use jpg or png images. PDF is still recommended
\usepackage[hidelinks]{hyperref} % add links inside PDF files
\usepackage{amsmath}  % Math fonts
\usepackage{amsfonts} %
\usepackage{amssymb}  %

@@

%% Citation package
\usepackage[square,numbers]{natbib}
\bibliographystyle{abbrvnat}
%\setcitestyle{authoryear,open={(},close={)}}

@@

\begin{abstract}
\textbf{gobba} is a dynamically typed and purely functional interpreted
programming language, heavily inspired from the OCaml,
Haskell and Scheme languages. It is based on Professors Gianluigi Ferrari and Francesca Levi's
minicaml interpreter example. The goal for gobba is to be a practical language
with built in support for scientific computing, solving some of the problems
that exist in other dynamically typed interpreted languages like python and
Javascript. It features static (lexical scoping), a simple but
effective module system, eager and lazy evaluation and an interactive didactical
REPL that shows completions and can show insights about each recursive evaluation step.
\end{abstract}

@@

\section{Syntax and Parser}
Lexing is achieved with \texttt{ocamllex}, the default tool for generating
scanners in OCaml. The parser is realized with the \textbf{Menhir} parser
generator library \cite{menhir}, and is documented using \textbf{Obelisk}, which
generates a clean text file containing the language grammar, available in
Appendix \ref{grammar}.
